---
title: "Geoms"
---

```{r setup, echo = FALSE, include = FALSE}
# Graphics
library("grid")
library("ggplot2")

# Lo de siempre
library("magrittr")
library("dplyr")
library("tidyr")

# Datos
library("colmaps")

# Algunas opciones de knitr y ggplot2
library("knitr")

link_geom <- function(geom_name){
  paste0("http://docs.ggplot2.org/current/", geom_name, ".html")
}

link_md <- function(x, link){
  if (is.null(link) || link == "") x else sprintf("[%s](%s)", x, link)
}

link_html <- function(x, link){
  if (is.null(link) || link == ""){
    x
  } else{
    sprintf('<a href="%s"> %s </a>', link, x)
  }
}

geom_slide_title <- function(geom_name){
  link_md(x = geom_name, link = link_geom(geom_name))
}

# knitr:::hook_plot_md_base
plot_hook <- function (x, options){
  # "Export" some knitr internal functions used in knitr:::hook_plot_md_base
  `%n%`       <- knitr:::`%n%`
  .upload.url <- knitr:::.upload.url
  .img.tag    <- knitr:::.img.tag
  css_align   <- knitr:::css_align

  if (options$fig.show == "animate")
    return(hook_plot_html(x, options))

  base <- opts_knit$get("base.url") %n% ""
  cap <- options$label

  link <- if (is.function(options$img.link)){
    options$img.link(options$label)
  } else if (is.character(options$img.link)){
    options$img.link
  }

  if (is.null(w <- options$out.width) & is.null(h <- options$out.height) &
      is.null(s <- options$out.extra) & options$fig.align == "default") {
    return(
      link_md(sprintf("![%s](%s%s) ", cap, base, .upload.url(x)), link)
    )
  }

  link_html(
    .img.tag(.upload.url(x), w, h, cap,
             c(s, sprintf("style=\"%s\"", css_align(options$fig.align)))),
    link)
}

knit_hooks$set(plot = plot_hook)

opts_chunk$set(message = FALSE,
               comment = "#>",
               dev.args = list(bg = "transparent"),
               img.link = link_geom)

theme_update(plot.background = element_rect(fill = "transparent",
                                            colour = "transparent"))

graph_path <- file.path("geoms", "graph")
```

```{r datos, echo = FALSE, include = FALSE, cache = TRUE}
volcano3d <- reshape2::melt(volcano)

names(volcano3d) <- c("x", "y", "z")

data.example <- data.frame(x  = c(1, 2, 5, 6, 8),
                           y  = c(3, 6, 2, 8, 7),
                           vx = c(1, 1.5, 0.8, 0.5, 1.3),
                           vy = c(0.2, 1.3, 1.7, 0.8, 1.4))

data("diamonds")
data("iris")
data("mtcars")

set.seed(54321)
df1 <- data.frame(a = rnorm(10, 25), b = rnorm(10, 0))
```

# Geoms

## geom_violin

```{r geom_violin}
ggplot(mtcars) + aes(y = mpg, x = factor(cyl)) + geom_violin()

```

## geom_dotplot

```{r geom_dotplot}
ggplot(mtcars) + aes(x = factor(cyl), y = mpg) +
  geom_dotplot(binaxis = "y", stackdir = "center", binwidth = 1)
```

## geom_boxplot

```{r geom_boxplot}
ggplot(mtcars) + aes(factor(cyl), mpg) + geom_boxplot()
```

## geom_bar

```{r geom_bar}
ggplot(mtcars) + aes(factor(cyl)) + geom_bar()
```

## geom_point

```{r geom_point}
ggplot(diamonds) + aes(price, depth) + geom_point()
```

## geom_bin2d

```{r geom_bin2d}
ggplot(diamonds) + aes(price, depth)   + geom_bin2d()
```

## geom_hex

```{r geom_hex}
#install.packages("hexbin")
ggplot(diamonds) + aes(price, depth) + stat_binhex()
```

## geom_points

```{r geom_points2}
ggplot(mpg) + aes(displ, hwy) + geom_point()
```

## geom_jitter

Points, jittered to reduce overplotting.

```{r geom_jitter}
set.seed(86420)
ggplot(mpg) + aes(displ, hwy) + geom_jitter()
```

## geom_quantile

```{r geom_quantile}
ggplot(mpg) + aes(displ, hwy) + geom_point() + geom_quantile()
```

## geom_smooth

```{r geom_smooth}
ggplot(mpg) + aes(displ, hwy) + geom_point() + geom_smooth()
```

## geom_density2d

```{r geom_density2d}
set.seed(98765)
ggplot(mpg) + aes(displ, hwy) + geom_jitter() + geom_density2d()
```

## geom_path

```{r geom_path}
ggplot(mpg) + aes(displ, hwy) + geom_point() + geom_path()

```

##  geom_rug

```{r geom_rug}
ggplot(mpg) + aes(displ, hwy) + geom_point() + geom_rug()
```

## ????

```{r base-boxplot}
boxplot(diamonds$price~ diamonds$color, plot = TRUE) %$%
  stats %>% matrix(5, 7) %>% t %>%  as.data.frame.matrix() %>% setNames(c("min", "q1", "med", "q3", "max")) %>%
  mutate(names = levels(diamonds$color)) -> intervalos
```

## geom_crossbar

```{r geom_crossbar}
ggplot(intervalos) + aes(x = names, ymin = q1, ymax = q3, y = med) +
  geom_crossbar()
```

## geom_linerange

```{r geom_linerange}
ggplot(intervalos) + aes(x = names, ymin = q1, ymax = q3, y = med) +
  geom_linerange()
```

## geom_pointrange

```{r geom_pointrange}
ggplot(intervalos) + aes(x = names, ymin = q1, ymax = q3, y = med) +
  geom_pointrange()
```

## geom_errorbar

```{r geom_errorbar}
ggplot(intervalos) + aes(x = names, ymin = q1, ymax = q3, y = med) +
  geom_errorbar()
```

## geom_errorbarh

```{r geom_errorbarh}
ggplot(intervalos) + aes(y = names, xmin = q1, xmax = q3, x = med) +
  geom_errorbarh()
```

## geom_ribbon

```{r geom_ribbon}
ggplot(intervalos) + aes(x = 1:7, ymin = q1, ymax = q3, y = med) +
  geom_ribbon(alpha = I(1/3)) + geom_pointrange()
```

## geom_area

```{r geom_area}
intervalos %>% select(-names) %>% gather(stat, value) %>%
  ggplot + aes(y = value, x = rep(1:7, 5), fill= stat) + geom_area()
```

## geom_line

```{r geom_line}
intervalos %>% select(-names) %>% gather(stat, value) %>%
  ggplot + aes(y = value, x = rep(1:7, 5), colour= stat) + geom_line()
```

## geom_density

```{r geom_density}
ggplot(mtcars) + aes(x = mpg) + geom_density()
```

## geom_freqpoly

```{r geom_freqpoly}
ggplot(mtcars) + aes(x = mpg) + geom_freqpoly(binwidth = 2)
```

## geom_histogram

```{r geom_histogram}
ggplot(mtcars) + aes(x = mpg) + geom_histogram(binwidth = 2)
```

## geom_blank

```{r geom_blank}
ggplot(mtcars) + aes(x = wt, y = mpg) + geom_point() +
  geom_abline(aes(intercept = a, slope = b), data = df1)
```

## geom_blank

```{r geom_blank-a}
ggplot(mtcars) + aes(x = wt, y = mpg, colour = factor(cyl), size = hp) + geom_blank() +
  geom_abline(aes(intercept = a, slope = b), data = df1)
```

## geom_abline

```{r geom_abline, eval = FALSE}
ggplot() +
  scale_x_continuous(name = "x", limits = c(0,5)) +
  scale_y_continuous(name = "y", limits = c(0,10)) +
  scale_linetype(name = "s") +
  geom_abline(data.example,
              mapping = aes(slope = vx, intercept = vy, linetype = factor(x))) +
  geom_hline(data = data.example, mapping = aes(yintercept = vy)) +
  geom_vline(data = data.example, mapping = aes(xintercept = vy))
```

## geom_abline

```{r geom_abline, echo = FALSE}
```

## geom_map {.smaller}

```{r geom_map}
require("colmaps")
map_df <- fortify(departamentos)
ggplot(map_df, aes(map_id = id)) +
  geom_map(map = map_df, color = "white", size = 0.1) +
  expand_limits(x = map_df$long, y = map_df$lat) +
  coord_map()
```

## geom_map {.smaller}

```{r colmap-cache, cache = TRUE}
require("colmaps")
colombia <- colmap(municipios) + 
  theme(plot.background = element_rect(fill = "transparent", 
                                       colour = "transparent"))
```

```{r colmap}
print(colombia)
```

## geom_polygon

```{r geom_polygon}
map_df %>% filter(id == 25) %>% ggplot + aes(x = long, y = lat) +
  geom_polygon() + coord_fixed()
```

## geom_raster

```{r geom_raster}
diamonds %$% table(color, clarity) %>% as.data.frame %>% ggplot +
  aes(x = color, y = clarity, fill = Freq) + geom_raster()
```

## geom_segment

```{r geom_segment}
ggplot(data.example) + aes(x = x, y = y, xend = x + vx, yend = y + vy) +
  geom_segment(arrow = arrow(), size = 2, color = "blue")
```

## geom_rect
  
```{r geom_rect}
ggplot(data.example) + aes(xmin = x, ymin = y, xmax = x + vx, ymax = y + vy) +
  geom_rect(fill = "blue")
```

## geom_step

```{r geom_step}
data.frame(x = sort(rnorm(47))) %>% ggplot + aes(seq_along(x), x) + geom_step()
```

## geom_text

```{r geom_text}
ggplot(mtcars) + aes(x = wt, y = mpg, label = rownames(mtcars)) + geom_text()
```

## geom_tile

```{r geom_tile}
diamonds %$% table(color, clarity) %>% as.data.frame %>% ggplot +
  aes(x = color, y = clarity, fill = Freq) + geom_tile()
```

## geom_countour

```{r geom_countour}
ggplot(volcano3d, aes(x, y, z = z)) +
  stat_contour(binwidth = 2, size = 0.5, colour = "grey50") +
  stat_contour(binwidth = 10, size = 1)
```
